\section{Behavioral Biometrics}\label{sec:behavioral-biometrics}
With the development of more and more powerful technology, there comes a need for sophisticated authentication methods.
One of a kind for authenticating a user with his individual physical patterns is static biometrics.
This approach is widely used nowadays in laptops or smartphones as a way for authentication.
The main concepts for this kind of biometrics are facial recognition, iris and fingerprint scanning.
However, these static methods raise big concerns.
First of all, the static approach is insecure, because when compromised, there is no way to change it dynamically.
Data are bounded in a way that cannot be deleted afterward.
Secondly, the big growth in technology, especially computer vision and cameras, raise a thread for facial recognition method, where the human face can be simply replicated based on a properly scanned subject head.
Moreover, this type of recognition raises concerns about human rights and privacy.
The IBM CEO, Arvinid Krishna in his letter~\cite{ibm_2020} to the US government deputies commit the withdrawal of facial recognition in the IBM technology stack.

The more sophisticated, private, and cost-effective implementation seems to be a behavioral biometric technique.
Behavioral biometrics are defined as "any quantifiable actions of a person. Such actions may not be unique to the person and may take a different amount of time to be exhibited by different individuals"~\cite{Yampolskiy2011}.
As stated by Tony Thomas --- these actions include voiceprints, signatures, typing patterns, keystroke patterns, or gait~\cite{thomas2020machine}.
The advantage of such an approach is the fact, that data collecting for further authentication can be gathered in a seamless manner, without the user's knowledge of the process.
Thanks to that, the properly designed system may be used to provide a continuous authorization of a user.
The malicious, hijacked session would be discovered because as stated by Yampolskiy --- "one of the defining characteristics of a behavioral biometric is the incorporation of the time dimension as a part of the behavioral signature"~\cite{Yampolskiy2011}, therefore the data is gathered and analyzed dynamically.
The domain can be divided into a couple of main categories, in which there exist the Human-Computer Interaction (HCI) based biometrics~\cite{Yampolskiy2011}.
In this approach, the data from different external devices is gathered along with its usage and then analyzed.
This device could be the keyboard with keystrokes analytics or mouse pointer usage.
This last seems to be the least discovered method due to time.
The mouse behavioral biometrics can find its usage in the web bot/web crawlers detection, as Wei et al.~\cite{a-deep-learning-approach-to-web-bot-detection-using-mouse-behavioral-biometrics} raise a topic of huge malicious bot traffic over the internet, which according to Bot Traffic Report 2016~\cite{bot-share-2016} reach to almost 30\% share of overall web bots traffic, thus the adoption of mouse behavioral biometrics would fit into the problem, hence "although web bots can
generate mouse events, it’s difficult for bots to perform mouse operations in a human manner"~\cite{a-deep-learning-approach-to-web-bot-detection-using-mouse-behavioral-biometrics}.
This works aims for broadening the knowledge in mouse behavioral biometrics.